Assessing glymphatic transport velocities by adjoint methods

### 2018-09-05 tex/paper.tex

@@

>>>>

The model considers multiple domains.

The sub-domains

The observations are taken form

\subsection*{Data}

\subsection*{Mathematical Model}
The objective function was defined as 
\begin{equation}
\min_{u,g} F = \quad \sum\limits_i\sp{n} \int\limits_{\Omega} |u(t_i) - u_{obs}(t_i)| \mathrm{d}\Omega + \frac{\alpha}{2} \int\limits_{0}\sp{T} || g ||_{L\sp{2}(\partial\Omega)} \mathrm{d}t + \frac{\beta}{2} \int\limits_{0}\sp{T} || \dot{g} ||_{L\sp{2}(\partial\Omega)}\mathrm{d}t 
\end{equation}
subjugated by   
\begin{equation}
\begin{aligned}
\frac{\partial u}{\partial t} = \nabla \cdot  D_i \nabla u \qquad \text{in} \qquad \Omega \times \left\lbrace 0 , T \right)  \\
u=g(t) \qquad \text{on} \qquad \partial\Omega  \times \left\lbrace 0 , T \right) 
\end{aligned}
\label{Eq::PDE}
\end{equation}
with the domain $\Omega$ contains three sub domains, each with a different diffusion coefficient. We denote the csf domain as $\Omega_1$, the grey matter as $\Omega_2$ and the white matter as $\Omega_3$.

Thus the determination of noise sensitivity was conducted by adding noise to the manufactured solution. The manufactured solution was obtained by forward computation of Eq.\ref{Eq::PDE} with following Dirichlet boundary condition
\begin{equation}
g(t)_{\partial \Omega_1} = 0.3 + 0.01t  \qquad  0 \leq t \leq 110.0.
\end{equation}
and diffusion coefficients 
\begin{equation}
D_c = 1000 
\end{equation}

The finite element

Dolfin adjoint was used to construct a reduced function,

The scipy optimize library was used, and minimize algorithm used L-BFGS-S.

@@

The L-BFGS-B algorithm does not scale the control parameters, thus the step size . This poses a problem with a large difference in the control parameters,
